Template for manuscript

### 2024-12-06 LakeMetabolism_project/Synthesis_21_22_23/report/manuscript.Rnw
Work on  manuscript

\documentclass[fleqn,11pt,lineno]{manuscript}
%%\usepackage{setspace}
%%\doublespacing
\usepackage{soul}

@@

Dissolved oxygen and water temperature measurements were yielded from EXO2 multiparameter
sondes, as described in section~\ref{subsec:design}. For the purpose
of estimating ecosystem metabolism, wind and irradiation data were yielded
from the QAS\_L automated weather station near Narsarsuaq, Greenland \citep{metadata}.

>>>>

\documentclass[fleqn,11pt,lineno]{manuscript}
%%\usepackage{setspace}
%%\doublespacing
\usepackage{soul}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,      
    urlcolor=blue,
    citecolor=blue,
    }

@@

Dissolved oxygen and water temperature measurements were yielded from EXO2 multiparameter
sondes, as described in section~\nameref{subsec:design}. For the purpose
of estimating ecosystem metabolism, wind and irradiation data were yielded
from the Programme for Monitoring of the Greenland Ice Sheet (PROMICE), providing automatic
weather station data \citep{Fausto:2021}.
The dataset named \texttt{QAS\_L\_hour.csv} originating from the QAS\_L automated weather station
near Narsarsuaq was downloaded from a
\href{https://dataverse.geus.dk/citation?persistentId=doi:10.22008/FK2/IW73UU}{public database}
provided by PROMICE \citep{metadata}.

The data preparation for estimating lake metabolism was done separately for each monitoring
period (16 September-24 September 2021, 22 June-3 July 2022, and 22 June-17 July 2023).

\subsubsection*{Sonde data}

First, the raw sonde data from each lake were imported and merged into
one dataset for a given monitoring period. The variables needed for lake metabolism
estimation were water temperature (\textdegree{}C) and
dissolved oxygen (mg/L). Next, an outlier analysis was performed by removing
values higher than three times the median absolute deviation of all values in a
sliding window of one day window size \citep{Luerig:2021}.
After outlier removal, the time series of water temperature and dissolved oxygen
were subsequently investigated for larger data gaps due to potential lack of sensor
measurements over certain periods.

To ensure overlapping estimation of lake metabolism, the data was subsequently
cut to achieve equal starting and ending time points for all lakes during a given
observation period. Due to large data gaps during the period of 2022, we chose
to keep as much complete days as possible in order to estimate the maximum
amount of days, rather than selecting the longest common monitoring period
for all lakes.

After cutting, missing values were replaced by a
weighted moving average, where the weights of observations around the
central value decrease exponentially \citep{Moritz:2017}.
For larger data gaps spanning over several hours, we chose
to not estimate lake metabolism for the affected days, rather than imputing these values.
